Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-26 article.tex

In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
performance of three other methods: standard (Pearson) correlation (PC),
generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
\textit{normal-2} network are shown for all methods in Figure
\ref{fig:curves}. Pearson correlation measures the unconditional linear
(in)dependence between variables and it should thus not be able to filter out
indirect interactions between neurons. GTE \citep{stetter2012model} was
proposed as a baseline for the challenge. This method builds on Transfer
Entropy to measure the association between two neurons. Unlike our approach, it
can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
a gene regulatory network inference method that was the best performer of the
DREAM5 challenge \cite{dream5paper}. When transposed to neural networks, this
method uses as a confidence score for the edge going from neuron $i$ to neuron
$j$ the importance score of variable $X_i$ in a Random Forests model trying to
predict $X_j$ from all variables in $X\setminus X_j$. To reduce computing times
of this method, we had to reduce each tree in the Random Forests model to a
maximum depth of 3. This constraint potentially severly affects the performance
of this method with respect to the use of fully grown trees. We nevertheless
provide these results for comparison purpose. PC and GENIE3 were both applied
on the same pre-filtered time series ($g \circ f_1$). For GENIE3, we
built 10000 trees per neuron and we used default settings for all other
parameters (except for the maximal tree depth). For GTE, we reproduced the
exact same setting (conditioning level and pre-processing) that was used for
the challenge.

>>>>

In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
performance of three other methods: standard (Pearson) correlation (PC),
generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
\textit{normal-2} network are shown for all methods in Figure
\ref{fig:curves}. Pearson correlation measures the unconditional linear
(in)dependence between variables and it should thus not be able to filter out
indirect interactions between neurons. GTE \citep{stetter2012model} was
proposed as a baseline for the challenge. This method builds on Transfer
Entropy to measure the association between two neurons. Unlike our approach, it
can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
a gene regulatory network inference method that was the best performer of the
DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
method uses as a confidence score for the edge going from neuron $i$ to neuron
$j$ the importance score of variable $X_i$ in a Random Forests model trying to
predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
computational cost of this method, we had to limit each tree in the Random
Forests model to a maximum depth of 3. This constraint potentially severly
affects the performance of this method with respect to the use of fully grown
trees. We nevertheless provide these results for comparison purpose. PC and
GENIE3 were both applied on the same pre-filtered time series ($g \circ
f_1$). For GENIE3, we built 10000 trees per neuron and we used default settings
for all other parameters (except for the maximal tree depth). For GTE, we
reproduced the exact same setting (conditioning level and pre-processing) that
was used for the challenge.
